GravExplain

### 2020-01-16 paper/paper_main.tex
some small edits in the intro

\section{Introduction}
A network of gravitational wave observatories around the world are .....

A Michelson interferometer is commonly used by gravitational wave research groups to demonstrate gravitational wave science to non-specialist audiences. 
These are typically table-top demonstrations

>>>>

\section{Introduction}

% general gw intro
In 2015 gravitational waves were observed for the first time from the merger of two black holes in a binary system.~\cite{GW150914} 
The observation, made by the Laser Interferometer Gravitational-wave Observatory~\citep[LIGO]{AdvancedLIGO:2015}, marked a breakthrough in modern astrophysics and provides a new means to observe the universe. 
Since 2015, the LIGO and Virgo~\cite{AdvancedVirgo:2015} observatories have made numerous detections of binary black hole~\cite{GW151226,GW170104,GW170814} and binary neutron star~\cite{GW170817,GW170817multi,GW190425} mergers. 
In recent years there has been an increased public interest in gravitaitonal-wave science. 
Many gravitational wave research groups around the world have produced demonstrations and activities to aid in explaining this topic to a general audience
Activites range from online data analysis tutorials,~\cite{GWOSC:online,LOSC:2015} hands-on demonstrations, phone apps,~\cite{LaserLabs:online,SciVR:online} and online games,~\cite{BlackHoleHunter:online} to exhibitions,\cite{L2URSSE} artistic interpretation, and musical performance \han{add refs}.

% what are gws and how do we detect them...
Gravitational waves are a prediction of Einstein's theory of general relativity. 
They are distrubances in spacetime caused by the accelleration of massive objects. 
The effect of gravitational waves is to change distances; a ``stretch and squeeze'' effect. 
Observatories such as LIGO, Virgo, and KAGRA~\cite{KAGRA:2013} are laser interferometers; they use the interference of laser light to measure changes in distance. 
The observatories themselves are extremely complex devices, however they are based on the Michelson interferometer. 
Table-top Michelson interferometers are commonly used by gravitational-wave research groups to demonstrate this science to non-specialist audiences~\cite{ThorLabsIFO,NikhefIFO}\han{add exhibit ifo when available} and they are often used in undergraduate lab experiments~\cite{UgoliniEtAl:2019}.

% continuous gws
To date the network of gravitational-wave observatories have observed short-duration transient signals~\cite{GWTC-1:2018,GWOSC:online}. 
However, these observatories are also searching for continuous gravitational waves; persistent, periodic signals which should be present in the data for many months or years. 
A prime target for these searches are rotating neutron stars. 
So far many searches have been made of LIGO and Virgo data, however no detection has been made so far.

% overview
In this article we describe how a Michelson interferometer can be used to demonstrate the search for continuous waves to a general audience. 
The techniques used are very similar to those used by researchers to search for continuous waves in LIGO and Virgo data. 
In section X we describe...... \han{add this in at the end}
